The Poisson approximate likelihood compared to the particle filter

### 2024-07-22 ms.Rnw
compilation, variable naming, and table variable read-in

\begin{document}

@@

graphics.off()      # close graphics windows
library(pomp)
library(magrittr)
library(plyr)
library(reshape2)
library(ggplot2)
library(scales)
library(foreach)
library(doParallel)
registerDoParallel()
stopifnot(packageVersion("pomp") >= "1.7")

RUN_LEVEL = 1
NP_MIF       = switch(RUN_LEVEL, 4, 50000)
NMIF         = switch(RUN_LEVEL, 4,  100)
ncores       = switch(RUN_LEVEL, 4,  36)
@

@@

<<OvOv-model>>=
# measurement model 
dmeas <- Csnippet("
                  if (ISNA(cases1)) {
                  lik = (give_log) ? 0 : 1;
                  } else {
                        lik =  dbinom(cases1, H1, q1, 1) +
                        dbinom(cases2, H2, q2, 1) +
                        dbinom(cases3, H3, q3, 1);

@@

# Set to MLE
params_stocks_stst_mle <- params_fixed

params_stocks_stst_mle["beta1"] <- 11.48
params_stocks_stst_mle["beta2"] <- 0.25
params_stocks_stst_mle["beta3"] <- 0.35
params_stocks_stst_mle["phi"] <- 0.14
params_stocks_stst_mle["beta11"] <- 0.16
params_stocks_stst_mle["sigma_q"] <- 0.021
params_stocks_stst_mle["sigma_xi"] <- 66.89
params_stocks_stst_mle["S10"] <- 0.047061
params_stocks_stst_mle["I10"] <- 0.000368
params_stocks_stst_mle["R10"] <- 0.015967
params_stocks_stst_mle["S20"] <- 0.015967
params_stocks_stst_mle["I20"] <- 0.000011
params_stocks_stst_mle["R20"] <- 0.003677
params_stocks_stst_mle["S30"] <- 0.237624
params_stocks_stst_mle["I30"] <- 0.000031
params_stocks_stst_mle["R30"] <- 0.001591
@

<<maximization1>>=
pt <- pomp::parameter_trans(
  log = c("beta1","beta2","beta3","sigma_q","sigma_xi"),
  logit=c("beta11"),
  barycentric=c("S10","I10","R10",
                "S20","I20","R20",
                "S30","I30","R30"),
  toEst= pomp::Csnippet("T_phi = logit(phi/(M_2PI));"),
  fromEst= pomp::Csnippet("phi = M_2PI*expit(T_phi);")
)

pomp(data = dat,
     times="time",
     t0=0,
     dmeasure = dmeas,
     rmeasure = rmeas,
     rprocess = discrete_time(step.fun = rproc, delta.t = 1/4),
     statenames = c("S1", "I1", "R1", "H1", 
                    "S2", "I2", "R2", "H2",
                    "S3", "I3", "R3", "H3", 
                    "q1", "q2", "q3"),
     paramnames = names(params_stocks_stst_mle),
     accumvars=c("H1", "H2", "H3"),
     rinit=rinit,
     partrans = pt,
     params = params_stocks_stst_mle
) -> sir

sir_panel <- panelPomp::panelPomp(list(unit1=sir),
                                  shared=NULL,
                                  specific=params_stocks_stst_mle |> 
                                    as.matrix() |>
                                    `colnames<-`("unit1")
)

require(doParallel)
cores <- ncores
registerDoParallel(cores)
mcopts <- list(set.seed=TRUE)

sir_box <- rbind(
  beta1=c(10,15),
  beta2=c(0.2,0.4),
  beta3=c(0.3,0.5),
  phi=c(0.01,0.3),
  beta11=c(0.1,0.2),
  sigma_q=c(0.001,0.1),
  sigma_xi=c(65,70),
  S10 = c(0.01,0.05),
  I10 = c(0.0001, 0.0005),
  R10 = c(0.01, 0.05),
  S20 = c(0.01,0.7),
  I20 = c(0.000001,0.00002),
  R20 = c(0.001,0.005),
  S30 = c(0.01,0.5),
  I30 = c(0.000001, 0.0001),
  R30 = c(0.0001,0.005)
)

bake(file = "output/round_01/ovov_mif_01.rds",{ 
  mifs_global <- foreach(i=1:cores,.packages='pomp', .options.multicore=mcopts) %dopar% {
    panelPomp::mif2(
      sir_panel,
      Np = NP_MIF,
      cooling.fraction.50 = 0.5,
      rw.sd = rw_sd(beta1=0.01,beta2=0.01,beta3=0.01,
                    beta11=0.01,phi=0.01,sigma_q=0.01,sigma_xi=0.01,
                    S10=ivp(0.24),I10=ivp(0.24),R10=ivp(0.24),
                    S20=ivp(0.24),I20=ivp(0.24),R20=ivp(0.24),
                    S30=ivp(0.24),I30=ivp(0.24),R30=ivp(0.24)),
      cooling.type = "geometric",
      Nmif = NMIF,
      shared.start = numeric(0),
      specific.start = starting,
      block = F
    ) 
  }
  mifs_global
})

bake(file = "output/round_01/ovov_01_el.rds",{
  el <- measlespkg::eval_logLik(mifs_global, ncores=cores, np_pf = NP_MIF, nreps=cores)
  el
})
@

<<maximization2>>=
sd           = 2/3
top_n_fits   = 12
# measurement model 
dmeas <- Csnippet("
                  if (ISNA(cases1)) {
                  lik = (give_log) ? 0 : 1;
                  } else {
                        lik =  dbinom(cases1, H1, q1, 1) +
                        dbinom(cases2, H2, q2, 1) +
                        dbinom(cases3, H3, q3, 1);

# Set to MLE
params_stocks_stst_mle <- params_fixed

params_stocks_stst_mle["beta1"] <- 11.48
params_stocks_stst_mle["beta2"] <- 0.25
params_stocks_stst_mle["beta3"] <- 0.35
params_stocks_stst_mle["phi"] <- 0.14
params_stocks_stst_mle["beta11"] <- 0.16
params_stocks_stst_mle["sigma_q"] <- 0.021
params_stocks_stst_mle["sigma_xi"] <- 66.89
params_stocks_stst_mle["S10"] <- 0.047061
params_stocks_stst_mle["I10"] <- 0.000368
params_stocks_stst_mle["R10"] <- 0.015967
params_stocks_stst_mle["S20"] <- 0.015967
params_stocks_stst_mle["I20"] <- 0.000011
params_stocks_stst_mle["R20"] <- 0.003677
params_stocks_stst_mle["S30"] <- 0.237624
params_stocks_stst_mle["I30"] <- 0.000031
params_stocks_stst_mle["R30"] <- 0.001591

@@

pomp(data = dat,
     times="time",
     t0=0,
     dmeasure = dmeas,
     rmeasure = rmeas,
     rprocess = discrete_time(step.fun = rproc, delta.t = 1/4),
     statenames = c("S1", "I1", "R1", "H1", 
                    "S2", "I2", "R2", "H2",
                    "S3", "I3", "R3", "H3", 
                    "q1", "q2", "q3"),
     paramnames = names(params_stocks_stst_mle),
     accumvars=c("H1", "H2", "H3"),
     rinit=rinit,
     partrans = pt,
     params = params_stocks_stst_mle
) -> sir

sir_panel <- panelPomp::panelPomp(list(unit1=sir),
                                  shared=NULL,
                                  specific=params_stocks_stst_mle |> 
                                    as.matrix() |>
                                    `colnames<-`("unit1")
)

require(doParallel)
cores <- ncores
registerDoParallel(cores)
mcopts <- list(set.seed=TRUE)

### Next-round code
el <- readRDS("output/round_01/ovov_01_el.rds")
x <- na.omit(el$fits)
score_total = x$logLik
ranking_total = order(score_total, decreasing = TRUE)[1:top_n_fits]

best_fits = dplyr::select(
  x[ranking_total,], -"logLik", -"se"
)

recycle_vec = sort(rep_len(1:top_n_fits, cores))
full_best_fit <- best_fits[recycle_vec, ]

coef_names <- colnames(full_best_fit)
colnames(full_best_fit) <- gsub(".{7}$","",coef_names)

starting_values <- vector(cores, mode="list")

for(i in 1:cores){
  t(full_best_fit[i, ])  |> 
    as.matrix() |>
    `colnames<-`("unit1") -> starting_values[[i]] 
}

mifs_global <- foreach(i=1:cores,.packages='pomp', .options.multicore=mcopts) %dopar% {
  panelPomp::mif2(
    sir_panel,
    Np = NP_MIF,
    cooling.fraction.50 = 0.5,
    rw.sd = rw_sd(beta1=0.01*sd,beta2=0.01*sd,beta3=0.01*sd,
                  beta11=0.01*sd,phi=0.01*sd,sigma_q=0.01*sd,sigma_xi=0.01*sd,
                  S10=ivp(0.24)*sd,I10=ivp(0.24)*sd,R10=ivp(0.24)*sd,
                  S20=ivp(0.24)*sd,I20=ivp(0.24)*sd,R20=ivp(0.24)*sd,
                  S30=ivp(0.24)*sd,I30=ivp(0.24)*sd,R30=ivp(0.24)*sd),
    cooling.type = "geometric",
    Nmif = NMIF,
    shared.start = numeric(0),
    specific.start = starting_values[[i]],
    block = F
  ) 
}

bake(file = "output/round_02/ovov_mif_02.rds",{ 
  mifs_global
})

bake(file = "output/round_02/ovov_02_el.rds",{
  el <- measlespkg::eval_logLik(mifs_global, ncores = cores, np_pf = NP_MIF, nreps=cores)
  el
})
@

@@

<<maximization3>>=
sd           = (2/3)^2
top_n_fits   = 12
# measurement model 
dmeas <- Csnippet("
                  if (ISNA(cases1)) {
                  lik = (give_log) ? 0 : 1;
                  } else {
                        lik =  dbinom(cases1, H1, q1, 1) +
                        dbinom(cases2, H2, q2, 1) +
                        dbinom(cases3, H3, q3, 1);

# Set to MLE
params_stocks_stst_mle <- params_fixed

params_stocks_stst_mle["beta1"] <- 11.48
params_stocks_stst_mle["beta2"] <- 0.25
params_stocks_stst_mle["beta3"] <- 0.35
params_stocks_stst_mle["phi"] <- 0.14
params_stocks_stst_mle["beta11"] <- 0.16
params_stocks_stst_mle["sigma_q"] <- 0.021
params_stocks_stst_mle["sigma_xi"] <- 66.89
params_stocks_stst_mle["S10"] <- 0.047061
params_stocks_stst_mle["I10"] <- 0.000368
params_stocks_stst_mle["R10"] <- 0.015967
params_stocks_stst_mle["S20"] <- 0.015967
params_stocks_stst_mle["I20"] <- 0.000011
params_stocks_stst_mle["R20"] <- 0.003677
params_stocks_stst_mle["S30"] <- 0.237624
params_stocks_stst_mle["I30"] <- 0.000031
params_stocks_stst_mle["R30"] <- 0.001591

pomp(data = dat,
     times="time",
     t0=0,
     dmeasure = dmeas,
     rmeasure = rmeas,
     rprocess = discrete_time(step.fun = rproc, delta.t = 1/4),
     statenames = c("S1", "I1", "R1", "H1", 
                    "S2", "I2", "R2", "H2",
                    "S3", "I3", "R3", "H3", 
                    "q1", "q2", "q3"),
     paramnames = names(params_stocks_stst_mle),
     accumvars=c("H1", "H2", "H3"),
     rinit=rinit,
     partrans = pt,
     params = params_stocks_stst_mle
) -> sir

sir_panel <- panelPomp::panelPomp(list(unit1=sir),
                                  shared=NULL,
                                  specific=params_stocks_stst_mle |> 
                                    as.matrix() |>
                                    `colnames<-`("unit1")
)

require(doParallel)
cores <- ncores
registerDoParallel(cores)
mcopts <- list(set.seed=TRUE)

### Next-round code
el <- readRDS("output/round_02/ovov_02_el.rds")
x <- na.omit(el$fits)
score_total = x$logLik
ranking_total = order(score_total, decreasing = TRUE)[1:top_n_fits]

best_fits = dplyr::select(
  x[ranking_total,], -"logLik", -"se"
)

recycle_vec = sort(rep_len(1:top_n_fits, cores))
full_best_fit <- best_fits[recycle_vec, ]

coef_names <- colnames(full_best_fit)
colnames(full_best_fit) <- gsub(".{7}$","",coef_names)

starting_values <- vector(cores, mode="list")

for(i in 1:cores){
  t(full_best_fit[i, ])  |> 
    as.matrix() |>
    `colnames<-`("unit1") -> starting_values[[i]] 
}

mifs_global <- foreach(i=1:cores,.packages='pomp', .options.multicore=mcopts) %dopar% {
  panelPomp::mif2(
    sir_panel,
    Np = NP_MIF,
    cooling.fraction.50 = 0.5,
    rw.sd = rw_sd(beta1=0.01*sd,beta2=0.01*sd,beta3=0.01*sd,
                  beta11=0.01*sd,phi=0.01*sd,sigma_q=0.01*sd,sigma_xi=0.01*sd,
                  S10=ivp(0.24)*sd,I10=ivp(0.24)*sd,R10=ivp(0.24)*sd,
                  S20=ivp(0.24)*sd,I20=ivp(0.24)*sd,R20=ivp(0.24)*sd,
                  S30=ivp(0.24)*sd,I30=ivp(0.24)*sd,R30=ivp(0.24)*sd),
    cooling.type = "geometric",
    Nmif = NMIF,
    shared.start = numeric(0),
    specific.start = starting_values[[i]],
    block = F
  ) 
}

bake(file = "output/round_03/ovov_mif_03.rds",{ 
  mifs_global
})

bake(file = "output/round_03/ovov_03_el.rds",{
  el <- measlespkg::eval_logLik(mifs_global, ncores = cores, np_pf = NP_MIF, nreps=cores)
  el
})
@

@@

\begin{table}[htbp]
  \centering
  \begin{threeparttable}
    \caption{Maximum likelihood estimation of parameters by PAL for three models \citep{wwr}, and by mif2 algorithm \citep{pomppackagepaper} for the OvOv model.
    \ed{LET'S DISCUSS WHETHER WE WANT TO SHOW JUST OV-OV HERE. IT WOULD BE SIMPLER.}
    }
    \label{tab:mlebywwr}
    \begin{tabular}{>{\raggedright\arraybackslash}p{2cm} *{3}{>{\centering\arraybackslash}p{1.5cm}} >{\centering\arraybackslash}p{2.5cm}}
      \toprule
      Parameter      & EqEq  & EqOv  & OvOv  & OvOv (\textbf{pomp})$^*$ \\
      \midrule
      \(\beta_1\)    & 12.15 & 12.74 & 11.48 & $\Sexpr{'test'}$\\
      \(\beta_2\)    & 0.22  & 0.21  & 0.25  & $\Sexpr{'test'}$\\
      \(\beta_3\)    & 0.34  & 0.31  & 0.35  & $\Sexpr{'test'}$\\
      \(\phi\)       & 0.017 & 0.14  & 0.14  & $\Sexpr{'test'}$\\
      \(\rho\)       & 0.022 & 0.19  & 0.16  & $\Sexpr{'test'}$\\
      \(\sigma^2_q\) & n/a   & 0.042 & 0.021 & $\Sexpr{'test'}$\\
      \(\sigma_\xi\) & n/a   & n/a   & 66.89 & $\Sexpr{'test'}$\\
      \addlinespace
      \multicolumn{1}{l}{\(S_{10}\)} & \multicolumn{3}{c}{$3876549^*$} & $5885201$\\
      \multicolumn{1}{l}{\(I_{10}\)} & \multicolumn{3}{c}{$30351$}     & $5041$\\
      \multicolumn{1}{l}{\(R_{10}\)} & \multicolumn{3}{c}{$1315221$}   & $721006$\\
      \multicolumn{1}{l}{\(S_{20}\)} & \multicolumn{3}{c}{$57139612$}  & $44546887$\\
      \multicolumn{1}{l}{\(I_{20}\)} & \multicolumn{3}{c}{$871$}       & $22$\\
      \multicolumn{1}{l}{\(R_{20}\)} & \multicolumn{3}{c}{$302852$}    & $26360811$\\
      \multicolumn{1}{l}{\(S_{30}\)} & \multicolumn{3}{c}{$19573727$}  & $4788420$\\
      \multicolumn{1}{l}{\(I_{30}\)} & \multicolumn{3}{c}{$2550$}      & $131$\\
      \multicolumn{1}{l}{\(R_{30}\)} & \multicolumn{3}{c}{$131092$}    & $65306$\\
      \midrule
      \addlinespace
      \textbf{AIC}  & $98866.65$ & $15154.75$ & $13778.08$ & $\Sexpr{'test'}$\\
      \addlinespace
      \bottomrule
    \end{tabular}
    \begin{tablenotes}
      \small
      \item[*] The initial distribution parameter \(\lambda_0 = (S_{10}, I_{10}, R_{10}, S_{20}, I_{20}, R_{20}, S_{30}, I_{30}, R_{30})\) are assumed to be \textbf{fixed} in \cite{wwr}. The results of the estimates of the OvOv (\textbf{pomp}) model are obtained by using the Iterated Filtering algorithm with 3 rounds and 100 iterations, 50,000 particles, and 36 replicates in each round with the top 12 best fits in terms of likelihood chosen to be the starting value for the next round. 
    \end{tablenotes}
  \end{threeparttable}
\end{table}

>>>>

\begin{document}
\SweaveOpts{concordance=TRUE}

@@

graphics.off()      # close graphics windows
library(pomp)
library(magrittr)
library(ggplot2)
library(scales)
library(foreach)
library(doParallel)
library(dplyr)
source("choose_n_fits.R")

RUN_LEVEL = 1
NP_MIF       = switch(RUN_LEVEL, 5000, 50000)
NMIF         = switch(RUN_LEVEL, 4,    100)
ncores       = switch(RUN_LEVEL, 4,    36)
top_n_fits   = switch(RUN_LEVEL, 1,    12)
@

@@

<<OvOv-model, include=False, massage=False, warning=False>>=
# measurement model 
dmeas <- Csnippet("
                  if (ISNA(cases1)) {
                  lik = (give_log) ? 0 : 1;
                  } else {
                        lik =  dbinom(cases1, H1, q1, 1) +
                        dbinom(cases2, H2, q2, 1) +
                        dbinom(cases3, H3, q3, 1);

@@

# WWR's rinit
rinit_wwr <- Csnippet("
    S1=3876549;
    S2=57139612;
    S3=19573727;
    I1=30351;
    I2=871;
    I3=2550;
    R1=1315221;
    R2=302852;
    R3=131092;
    H1 = 0;
    H2 = 0;
    H3 = 0;
")

# x <- c(3876549,57139612,19573727,30351,871,2550,1315221,302852,131092)
# x/sum(x)

# Set to MLE
wwr_mle <- params_fixed

wwr_mle <- c(params_fixed, 
             "beta1" = 11.48,
             "beta2" = 0.25,
             "beta3" = 0.35,
             "phi" = 0.14,
             "beta11" = 0.16,
             "sigma_q" = 0.021,
             "sigma_xi" = 66.89,
             "S10" = 4.706102e-02,
             "S20" = 6.936707e-01,
             "S30" = 2.376236e-01,
             "I10" = 3.684589e-04,
             "I20" = 1.057388e-05,
             "I30" = 3.095681e-05,
             "R10" = 1.596669e-02,
             "R20" = 3.676601e-03,
             "R30" = 1.591447e-03)

@@

pomp(data = dat,
     times="time",
     t0=0,
     dmeasure = dmeas,
     rmeasure = rmeas,
     rprocess = discrete_time(step.fun = rproc, delta.t = 1/4),
     statenames = c("S1", "I1", "R1", "H1", 
                    "S2", "I2", "R2", "H2",
                    "S3", "I3", "R3", "H3", 
                    "q1", "q2", "q3"),
     paramnames = names(wwr_mle),
     accumvars=c("H1", "H2", "H3"),
     rinit=rinit,
     partrans = pt,
     params = wwr_mle
) -> sir

sir_panel <- panelPomp::panelPomp(list(unit1=sir),
                                  shared=NULL,
                                  specific=wwr_mle |> 
                                    as.matrix() |>
                                    `colnames<-`("unit1")
)
@

<<maximization1, include=False, massage=False, warning=False>>=
set.seed(123)
sir_box <- rbind(
  beta1=c(10,15),
  beta2=c(0.2,0.4),
  beta3=c(0.3,0.5),
  phi=c(0.01,0.3),
  beta11=c(0.1,0.2),
  sigma_q=c(0.001,0.1),
  sigma_xi=c(65,70),
  S10 = c(0.01,0.05),
  I10 = c(0.0001, 0.0005),
  R10 = c(0.01, 0.05),
  S20 = c(0.01,0.7),
  I20 = c(0.000001,0.00002),
  R20 = c(0.001,0.005),
  S30 = c(0.01,0.5),
  I30 = c(0.000001, 0.0001),
  R30 = c(0.0001,0.005)
)

require(doParallel)
registerDoParallel(ncores)
mcopts <- list(set.seed=TRUE)

bake(file = "output/round_01/ovov_mif_01.rds",{ 
  mifs_global_01 <- foreach(i=1:ncores,.packages='pomp', .options.multicore=mcopts) %dopar% {
    set.seed(112*i)
    panelPomp::mif2(
      sir_panel,
      Np = NP_MIF,
      cooling.fraction.50 = 0.5,
      rw.sd = rw_sd(beta1=0.01,beta2=0.01,beta3=0.01,
                    beta11=0.01,phi=0.01,sigma_q=0.01,sigma_xi=0.01,
                    S10=ivp(0.24),I10=ivp(0.24),R10=ivp(0.24),
                    S20=ivp(0.24),I20=ivp(0.24),R20=ivp(0.24),
                    S30=ivp(0.24),I30=ivp(0.24),R30=ivp(0.24)),
      cooling.type = "geometric",
      Nmif = NMIF,
      shared.start = numeric(0),
      specific.start = starting,
      block = F
    ) 
  }
  mifs_global_01
})

bake(file = "output/round_01/ovov_01_el.rds",{
  el <- measlespkg::eval_logLik(mifs_global_01, ncores=ncores, np_pf = NP_MIF, nreps=ncores)
  el
})
@

<<maximization2, include=False, massage=False, warning=False>>=
set.seed(1234)
sd_02           = 2/3

el_01 <- readRDS("output/round_01/ovov_01_el.rds")
starting_values_02 <- choose_n_fits(el_01, top_n_fits, ncores)

require(doParallel)
registerDoParallel(ncores)
mcopts <- list(set.seed=TRUE)

bake(file = "output/round_02/ovov_mif_02.rds",{ 
  mifs_global_02 <- foreach(i=1:ncores,.packages='pomp', .options.multicore=mcopts) %dopar% {
  panelPomp::mif2(
    sir_panel,
    Np = NP_MIF,
    cooling.fraction.50 = 0.5,
    rw.sd = rw_sd(beta1=0.01*sd_02,beta2=0.01*sd_02,beta3=0.01*sd_02,
                  beta11=0.01*sd_02,phi=0.01*sd_02,sigma_q=0.01*sd_02,sigma_xi=0.01*sd_02,
                  S10=ivp(0.24)*sd_02,I10=ivp(0.24)*sd_02,R10=ivp(0.24)*sd_02,
                  S20=ivp(0.24)*sd_02,I20=ivp(0.24)*sd_02,R20=ivp(0.24)*sd_02,
                  S30=ivp(0.24)*sd_02,I30=ivp(0.24)*sd_02,R30=ivp(0.24)*sd_02),
    cooling.type = "geometric",
    Nmif = NMIF,
    shared.start = numeric(0),
    specific.start = starting_values_02[[i]],
    block = F
  ) 
}
  mifs_global_02
})

bake(file = "output/round_02/ovov_02_el.rds",{
  el <- measlespkg::eval_logLik(mifs_global_02, ncores = ncores, np_pf = NP_MIF, nreps=ncores)
  el
})
@

@@

<<maximization3, include=False, massage=False, warning=False>>=
set.seed(12345)
sd_03           = (2/3)^2

el_02 <- readRDS("output/round_02/ovov_02_el.rds")
starting_values_03 <- choose_n_fits(el_02, top_n_fits, ncores)

require(doParallel)
registerDoParallel(ncores)
mcopts <- list(set.seed=TRUE)

bake(file = "output/round_03/ovov_mif_03.rds",{ 
  mifs_global_03 <- foreach(i=1:ncores,.packages='pomp', .options.multicore=mcopts) %dopar% {
  panelPomp::mif2(
    sir_panel,
    Np = NP_MIF,
    cooling.fraction.50 = 0.5,
    rw.sd = rw_sd(beta1=0.01*sd_03,beta2=0.01*sd_03,beta3=0.01*sd_03,
                  beta11=0.01*sd_03,phi=0.01*sd_03,sigma_q=0.01*sd_03,sigma_xi=0.01*sd_03,
                  S10=ivp(0.24)*sd_03,I10=ivp(0.24)*sd_03,R10=ivp(0.24)*sd_03,
                  S20=ivp(0.24)*sd_03,I20=ivp(0.24)*sd_03,R20=ivp(0.24)*sd_03,
                  S30=ivp(0.24)*sd_03,I30=ivp(0.24)*sd_03,R30=ivp(0.24)*sd_03),
    cooling.type = "geometric",
    Nmif = NMIF,
    shared.start = numeric(0),
    specific.start = starting_values_03[[i]],
    block = F
  ) 
}
  mifs_global_03
})

bake(file = "output/round_03/ovov_03_el.rds",{
  el <- measlespkg::eval_logLik(mifs_global_03, ncores = ncores, np_pf = NP_MIF, nreps=ncores)
  el
})
@

<<estimated-mle, include=False, massage=False, warning=False>>=
mif_el <- readRDS("output/round_03/ovov_03_el.rds") # Can be changed if more rounds needed
est_mle_vec <- mif_el$fits[which.max(mif_el$fits$logLik),]
@

@@

\begin{table}[htbp]
  \centering
  \begin{threeparttable}
    \caption{Maximum likelihood estimation of parameters by PAL for three models \citep{wwr}, and by mif2 algorithm \citep{pomppackagepaper} for the OvOv model.
    \ed{LET'S DISCUSS WHETHER WE WANT TO SHOW JUST OV-OV HERE. IT WOULD BE SIMPLER.}
    }
    \label{tab:mlebywwr}
    \begin{tabular}{>{\raggedright\arraybackslash}p{2cm} *{3}{>{\centering\arraybackslash}p{1.5cm}} >{\centering\arraybackslash}p{2.5cm}}
      \toprule
      Parameter      & EqEq  & EqOv  & OvOv  & OvOv (\textbf{pomp})$^*$ \\
      \midrule
      \(\beta_1\)    & 12.15 & 12.74 & 11.48 & $\Sexpr{est_mle_vec["beta1[unit1]"]}$\\
      \(\beta_2\)    & 0.22  & 0.21  & 0.25  & $\Sexpr{est_mle_vec["beta2[unit1]"]}$\\
      \(\beta_3\)    & 0.34  & 0.31  & 0.35  & $\Sexpr{est_mle_vec["beta3[unit1]"]}$\\
      \(\phi\)       & 0.017 & 0.14  & 0.14  & $\Sexpr{est_mle_vec["phi[unit1]"]}$\\
      \(\rho\)       & 0.022 & 0.19  & 0.16  & $\Sexpr{est_mle_vec["rho[unit1]"]}$\\
      \(\sigma^2_q\) & n/a   & 0.042 & 0.021 & $\Sexpr{est_mle_vec["sigma_q[unit1]"]}$\\
      \(\sigma_\xi\) & n/a   & n/a   & 66.89 & $\Sexpr{est_mle_vec["sigma_xi[unit1]"]}$\\
      \addlinespace
      \multicolumn{1}{l}{\(S_{10}\)} & \multicolumn{3}{c}{$3876549^*$} & $$\Sexpr{est_mle_vec["S10[unit1]"]}$$\\
      \multicolumn{1}{l}{\(I_{10}\)} & \multicolumn{3}{c}{$30351$}     & $$\Sexpr{est_mle_vec["I10[unit1]"]}$$\\
      \multicolumn{1}{l}{\(R_{10}\)} & \multicolumn{3}{c}{$1315221$}   & $$\Sexpr{est_mle_vec["R10[unit1]"]}$$\\
      \multicolumn{1}{l}{\(S_{20}\)} & \multicolumn{3}{c}{$57139612$}  & $$\Sexpr{est_mle_vec["S20[unit1]"]}$$\\
      \multicolumn{1}{l}{\(I_{20}\)} & \multicolumn{3}{c}{$871$}       & $$\Sexpr{est_mle_vec["sigma_xi[unit1]"]}$$\\
      \multicolumn{1}{l}{\(R_{20}\)} & \multicolumn{3}{c}{$302852$}    & $$\Sexpr{est_mle_vec["sigma_xi[unit1]"]}$$\\
      \multicolumn{1}{l}{\(S_{30}\)} & \multicolumn{3}{c}{$19573727$}  & $$\Sexpr{est_mle_vec["sigma_xi[unit1]"]}$$\\
      \multicolumn{1}{l}{\(I_{30}\)} & \multicolumn{3}{c}{$2550$}      & $$\Sexpr{est_mle_vec["sigma_xi[unit1]"]}$$\\
      \multicolumn{1}{l}{\(R_{30}\)} & \multicolumn{3}{c}{$131092$}    & $$\Sexpr{est_mle_vec["sigma_xi[unit1]"]}$$\\
      \midrule
      \addlinespace
      \textbf{AIC}  & $98866.65$ & $15154.75$ & $13778.08$ & $\Sexpr{(-2)*((length(wwr_mle) - length(params_fixed)) - est_mle_vec["logLik"])}$\\
      \addlinespace
      \bottomrule
    \end{tabular}
    \begin{tablenotes}
      \small
      \item[*] The initial distribution parameter \(\lambda_0 = (S_{10}, I_{10}, R_{10}, S_{20}, I_{20}, R_{20}, S_{30}, I_{30}, R_{30})\) are assumed to be \textbf{fixed} in \cite{wwr}. The results of the estimates of the OvOv (\textbf{pomp}) model are obtained by using the Iterated Filtering algorithm with 3 rounds and 100 iterations, 50,000 particles, and 36 replicates in each round with the top 12 best fits in terms of likelihood chosen to be the starting value for the next round. 
    \end{tablenotes}
  \end{threeparttable}
\end{table}
